Repeatability Test

### 2017-06-16 pt_characterization/rep_check/u_s_time.tex
June 16 Draft

\begin{table}[h]
\begin{center}
\begin{tabular}{|p{2cm}|p{3cm}|p{3cm}|p{4cm}|p{3.5cm}|} \hline
Machine & Task Length (sec) & Description & Experiment Period & Relevant \linebreak Histograms\\ \hline
{\tt sodb9} &  INC96$\sim$INC256 & 1000 samples, each & 2017-05-24 $\sim$ 2017-06-06 & 
Figs.~\ref{fig:ut_hist3}, \ref{fig:inc224_ut_hist}, and~\ref{fig:inc256_ut_hist}\\ \hline
					&  INC3, 6, 12, 24, 48, 72, 80, 88, 104, 112 & 1000 samples, each & 2017-06-07 $\sim$ 2017-06-14 & Figs.~\ref{fig:inc3_ut_hist}, ~\ref{fig:inc6_ut_hist}, ~\ref{fig:inc12_ut_hist}, ~\ref{fig:inc24_ut_hist},
~\ref{fig:inc48_ut_hist}, ~\ref{fig:inc72_ut_hist}, ~\ref{fig:inc80_ut_hist}, ~\ref{fig:inc88_ut_hist}, ~\ref{fig:inc104_ut_hist}, and ~\ref{fig:inc112_ut_hist}\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Notes on experiment runs used for histograms\label{tab:exp_notes4}}
\end{table}

@@

\begin{figure}[hp!]
	\centering
	\subfigure[User time frequency on INC104]{
		\includegraphics[scale=0.43]{u_s_time/104_sec_ut_hist.eps}
		\label{fig:inc104_ut_hist}
	}
	\subfigure[User time frequency on INC112]{
		\includegraphics[scale=0.43]{u_s_time/112_sec_ut_hist.eps}
		\label{fig:inc112_ut_hist}
	}
	\caption{User Time Histograms of INC104 and INC112~\label{fig:ut_hist5}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[User time frequency on INC128]{
		\includegraphics[scale=0.43]{u_s_time/128_sec_ut_hist2.eps}
		\label{fig:inc128_ut_hist2}
	}
	\subfigure[User time frequency on INC160]{
		\includegraphics[scale=0.43]{u_s_time/160_sec_ut_hist.eps}
		\label{fig:inc160_ut_hist}
	}
	\subfigure[User time frequency on INC192]{
		\includegraphics[scale=0.43]{u_s_time/192_sec_ut_hist.eps}
		\label{fig:inc192_ut_hist}
	}
	\caption{User Time Histograms of INC128 ... INC192~\label{fig:ut_hist6}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[User time frequency on INC224]{
		\includegraphics[scale=0.43]{u_s_time/224_sec_ut_hist.eps}
		\label{fig:inc224_ut_hist}
	}
	\subfigure[User time frequency on INC256]{
		\includegraphics[scale=0.43]{u_s_time/256_sec_ut_hist2.eps}
		\label{fig:inc256_ut_hist}
	}
	\subfigure[User time frequency on INC512 (with one extreme outlier of 513,259 msec removed)]{
		\includegraphics[scale=0.43]{u_s_time/512_sec_ut_hist.eps}
		\label{fig:inc512_ut_hist}
	}
	\subfigure[User time frequency on INC1024]{
		\includegraphics[scale=0.43]{u_s_time/1024_sec_ut_hist.eps}
		\label{fig:inc1024_ut_hist}
	}
	\caption{User Time Histograms of INC224 ... INC256~\label{fig:ut_hist7}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[User time frequency on INC2048]{
		\includegraphics[scale=0.43]{u_s_time/2048_sec_ut_hist.eps}
		\label{fig:inc2048_ut_hist}
	}
	\subfigure[User time frequency on INC4096]{
		\includegraphics[scale=0.43]{u_s_time/4096_sec_ut_hist.eps}
		\label{fig:inc4096_ut_hist}
	}
	\caption{User Time Histograms of INC2048 and INC4096~\label{fig:ut_hist8}}
\end{figure}

>>>>

\begin{table}[h]
\begin{center}
\begin{tabular}{|p{2cm}|p{3cm}|p{3cm}|p{4cm}|p{3.5cm}|} \hline
Machine & Task Length (sec) & Description & Experiment Period & Relevant \linebreak Histograms\\ \hline
{\tt sodb9} &  INC96$\sim$INC256 & 1000 samples, each & 2017-05-24 $\sim$ 2017-06-06 & 
Figs.~\ref{fig:ut_hist3}, \ref{fig:inc224_ut_hist}, and~\ref{fig:inc256_ut_hist}\\ \hline
					&  INC3, 6, 12, 24, 48, 72, 80, 88, 104, 112, and 120 & 1000 samples, each & 2017-06-07 $\sim$ 2017-06-16 & Figs.~\ref{fig:inc3_ut_hist}, ~\ref{fig:inc6_ut_hist}, ~\ref{fig:inc12_ut_hist}, ~\ref{fig:inc24_ut_hist},
~\ref{fig:inc48_ut_hist}, ~\ref{fig:inc72_ut_hist}, ~\ref{fig:inc80_ut_hist}, ~\ref{fig:inc88_ut_hist}, ~\ref{fig:inc104_ut_hist},~\ref{fig:inc112_ut_hist}, and~\ref{fig:inc120_ut_hist}\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Notes on experiment runs used for histograms\label{tab:exp_notes4}}
\end{table}

@@

\begin{figure}[hp!]
	\centering
	\subfigure[User time frequency on INC104]{
		\includegraphics[scale=0.43]{u_s_time/104_sec_ut_hist.eps}
		\label{fig:inc104_ut_hist}
	}
	\subfigure[User time frequency on INC112]{
		\includegraphics[scale=0.43]{u_s_time/112_sec_ut_hist.eps}
		\label{fig:inc112_ut_hist}
	}
	\subfigure[User time frequency on INC120]{
		\includegraphics[scale=0.43]{u_s_time/120_sec_ut_hist.eps}
		\label{fig:inc120_ut_hist}
	}
	\subfigure[User time frequency on INC128]{
		\includegraphics[scale=0.43]{u_s_time/128_sec_ut_hist2.eps}
		\label{fig:inc128_ut_hist2}
	}
	\caption{User Time Histograms of INC104 and INC128~\label{fig:ut_hist5}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[User time frequency on INC160]{
		\includegraphics[scale=0.43]{u_s_time/160_sec_ut_hist.eps}
		\label{fig:inc160_ut_hist}
	}
	\subfigure[User time frequency on INC192]{
		\includegraphics[scale=0.43]{u_s_time/192_sec_ut_hist.eps}
		\label{fig:inc192_ut_hist}
	}
	\subfigure[User time frequency on INC224]{
		\includegraphics[scale=0.43]{u_s_time/224_sec_ut_hist.eps}
		\label{fig:inc224_ut_hist}
	}
	\subfigure[User time frequency on INC256]{
		\includegraphics[scale=0.43]{u_s_time/256_sec_ut_hist2.eps}
		\label{fig:inc256_ut_hist}
	}
	\caption{User Time Histograms of INC160 ... INC256~\label{fig:ut_hist6}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[User time frequency on INC512 (with one extreme outlier of 513,259 msec removed)]{
		\includegraphics[scale=0.43]{u_s_time/512_sec_ut_hist.eps}
		\label{fig:inc512_ut_hist}
	}
	\subfigure[User time frequency on INC1024]{
		\includegraphics[scale=0.43]{u_s_time/1024_sec_ut_hist.eps}
		\label{fig:inc1024_ut_hist}
	}
	\subfigure[User time frequency on INC2048]{
		\includegraphics[scale=0.43]{u_s_time/2048_sec_ut_hist.eps}
		\label{fig:inc2048_ut_hist}
	}
	\subfigure[User time frequency on INC4096]{
		\includegraphics[scale=0.43]{u_s_time/4096_sec_ut_hist.eps}
		\label{fig:inc4096_ut_hist}
	}
	\caption{User Time Histograms of INC512 ... INC4096~\label{fig:ut_hist7}}
\end{figure}
